### 2020-08-12 manuscript/manuscript.rmd
minor rewording, re-executed manuscript code

  theme_set(theme_pubr())
  source( "functions.R" )

@@

These results further clarify when analyses support Porifera-sister (*e.g.* Philippe2009, Whelan2017). Outgroup sampling must be restricted (Choanimalia), a very large number of site categories must be used (unconstrained CAT, giving hundreds of categories), and a simplistic Poisson rather than GTR exchange matrix must be used. Analyses under other conditions either support Ctenophora-sister or are unresolved.

@@

>>>>

  theme_set(theme_pubr())
  source( "functions.R" )
  source( "phylobayes.R" )

@@

These results further clarify when analyses support Porifera-sister (*e.g.* Philippe2009, Whelan2017). Outgroup sampling must be restricted (Choanimalia), a Poisson rather than GTR exchange matrix must be used, and a very large number of site categories must be used (unconstrained CAT, giving hundreds of equilibrium frequency categories). Analyses under other conditions either support Ctenophora-sister or are unresolved. This is very consistent across published analyses and our new panels of analyses. The question, then, isn't why similar analyses give different results, but how we should interpret variation in results when we run analyses that differ in these respects. If we fix the first two features to conditions that are necessary for Porifera-sister support (Choanimalia taxon sampling and a Poisson exchange matrix), there are several things we can learn from examining how the number of equilibrium frequency categories impacts results that sheds light on interpretation of those results.

@@

```{r n_cat_render, fig.width=6, fig.height=12}

# gg_n_cat

**Extended Data Fig. 3.5** The impact of adding a large number of categories.
